Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large and Kmeans model with 
\(K=1000\).
We use embedding dimension 1024,  4 transformer 
encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
use layer norm after the cross attention module. 
We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
sharing embeddings does slightly better than sharing embeddings. The LM of small version TSELM-S uses 
embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM. The conformer encoder is composed of 
6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
\(d\) = 768 with 12 layers and 16 heads. We use AdamW as 
our optimizer for all the experiments. The learning rate 
is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L.

@@

It is shown that metrics like PESQ, SI-SNR, STOI do not reflect speech quality of output of 
vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
\cite{tokensplit,selm}. To measure the speech quality, 
speech intelligibility, and speech similarity.  We have used

>>>>

We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large and Kmeans model with 
\(K=1000\).
We use embedding dimension 1024,  4 transformer 
encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
use layer norm after the cross attention module. 
We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
sharing embeddings does slightly better than sharing embeddings. The LM of small version TSELM-S uses 
embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM. The conformer encoder is composed of 
6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
\(d\) = 768 with 12 layers and 16 heads. We use AdamW as 
our optimizer for all the experiments. The learning rate 
is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We use 8 16Gb ram GPUs. Our batch size is set to 128. We train the model for 40k steps.

@@

It is shown that metrics like PESQ, SI-SNR, STOI do not reflect speech quality of output of 
vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
\cite{tokensplit,selm}. We used DNSMOS \cite{dnsmos} to measure the speech quality, and differential 
word error 
rate (dWER) \cite{dwer} to measure the speech intelligibility. For speaker similarity, we use the 
public WeSpeaker \cite{wespeaker}.
